CODE CHECK

### 2020-05-26 codecheck-paper.Rmd
add stodden and whitaker references
potentially useful for classification

- **Principles**: https://codecheck.org.uk/
- relation to "proper" citation of data and software, and depositing of data and software in suitable repos _besides_ the bundle for CODE CHECK: do it, only provide the concrete analysis script for the check
- **Why is it useful?**
  - reduce the barrier to evaluating non-text parts of research
  - acknowledges different skill sets and existing high load on reviewers
  - CC breaks problem that publishers staff expertise today is not likely to suffice
  - engaging ECRs is a perfet fit (they are up-to-date in methods, are introduced to peer review)
  - relation to research compendia? point it out for authors unsure about how to structure their workflow
  - CrossRef and Publons and ORCID have features around reviews
  - shifting burden from reviewer to author (but not too much)
- keynote https://doi.org/10.7557/5.4963: in discussion, the speaker mentioned value of peer review for "baseline reassurance", i.e. a paper has at least been checked by someone with an understanding, to increase trust especially if looking at papers from other disciplines
- **report** must fulfil some requirements to make clear what is really checked and not mislead - readers will have very different understandings of a green checkmark!
- reproducibility is hard https://twitter.com/annakrystalli/status/1144176149859377152?ref_src=twsrc%5Etfw > code check gives at least some benefits

>>>>

- **Principles**: https://codecheck.org.uk/
- relation to "proper" citation of data and software, and depositing of data and software in suitable repos _besides_ the bundle for CODE CHECK: do it, only provide the concrete analysis script for the check
- **Why is it useful?**
  - reduce the barrier to evaluating non-text parts of research
  - acknowledges different skill sets and existing high load on reviewers
  - CC breaks problem that publishers staff expertise today is not likely to suffice
  - engaging ECRs is a perfet fit (they are up-to-date in methods, are introduced to peer review)
  - relation to research compendia? point it out for authors unsure about how to structure their workflow
  - CrossRef and Publons and ORCID have features around reviews
  - shifting burden from reviewer to author (but not too much)
- keynote https://doi.org/10.7557/5.4963: in discussion, the speaker mentioned value of peer review for "baseline reassurance", i.e. a paper has at least been checked by someone with an understanding, to increase trust especially if looking at papers from other disciplines
- **report** must fulfil some requirements to make clear what is really checked and not mislead - readers will have very different understandings of a green checkmark!
- reproducibility is hard https://twitter.com/annakrystalli/status/1144176149859377152?ref_src=twsrc%5Etfw > code check gives at least some benefits
- what are the requirements / level or reproducibility required or checked?
  - [Stodden et al., 2013](https://stodden.net/icerm_report.pdf): five-level hierarchy of research - reviewable, replicable, confirmable, auditable, and open or reproducible
  - [Whitaker 2017](https://figshare.com/articles/Showing_your_working_A_guide_to_reproducible_neuroimaging_analyses/4244996/2): reproducible, generalisable, replicability, robustness
